Evaluating `Graphical Perception' with CNNs

### 2018-03-30 PAPER/06_bars_and_framed_rectangles_experiment.tex
More updates.

As identified by Cleveland and McGill, the bar and framed rectangle experiment is closely related to Weber's law. This psychophysics law states that perceivable difference within a distribution is proportional to the initial size of the distribution. Weber's law goes hand-in-hand with Fechner's law. We conduct an additional experiment based on the original illustrations of the Weber-Fechner law to investigate whether this law can be applied to computational perception of our classifiers (Fig.~\ref{fig:webers_law}).

@@

>>>>

As identified by Cleveland and McGill, the bar and framed rectangle experiment is closely related to Weber's law. This psychophysics law states that perceivable difference within a distribution is proportional to the initial size of the distribution. Weber's law goes hand-in-hand with Fechner's law. We conduct an additional experiment based on the original illustrations of the Weber-Fechner law to investigate whether this law can be applied to computational perception of our classifiers (Fig.~\ref{tab:weber_law}).

@@

	\bottomrule
\end{tabular}
}
\label{tab:weber_law}
\end{table}
